\sysfull

### 2018-04-17 paper/hwswsetup.tex
pass over hw

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{| r|r|r | p{0.65\columnwidth} |}
		\hline
		Application & No. tasks & SLOC & Description \\
		\hline\hline
        \textbf{ar} & & & Activity recognition using a nearest neighbor
classifier with a deterministic input from a randomly-generated sequence of
accelerometer data\\
		\hline
        \textbf{bc} & & & Counts set bits in a pseudo-random sequence of bytes
using several algorithms and compares results for correctness\\
		\hline
        \textbf{cuckoo} & & & Inserts and queries a sequence of pseudo-random
values in a Cuckoo filter, a set membership data structure with deletion\\
		\hline
        \textbf{dijkstra} &  & & Dijkstra shortest path algorithm executed on a
predefined adjacency matrix\\
		\hline
        \textbf{fft} & & & Fast Fourier Transform on three pre-generated 128
sample vectors\\
		\hline
		\textbf{sort} & & & Selection sort of a fixed sequence of numbers\\
		\hline
	\end{tabular}
\caption{Description and characteristics of benchmark applications used to
evaluate \sys. \todo{SLOC and Number of Tasks}{Amjad}}
\label{table:benchmark_table}
\end{table}

>>>>

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{| r|r|r | p{0.65\columnwidth} |}
		\hline
		Application & No. tasks & SLOC & Description \\
		\hline\hline
        \textbf{ar} &10 &500 & Activity recognition using a nearest neighbor
classifier with a deterministic input from a randomly-generated sequence of
accelerometer data\\
		\hline
        \textbf{bc} &10 &419 & Counts set bits in a pseudo-random sequence of bytes
using several algorithms and compares results for correctness\\
		\hline
        \textbf{cuckoo} &14 &499 & Inserts and queries a sequence of pseudo-random
values in a Cuckoo filter, a set membership data structure with deletion\\
		\hline
        \textbf{dijkstra} &5 &227 & Dijkstra shortest path algorithm executed on a
predefined adjacency matrix\\
		\hline
        \textbf{fft} &8 &516 & Fast Fourier Transform on three pre-generated 128
sample vectors\\
		\hline
		\textbf{sort} &181 &4 & Selection sort of a fixed sequence of numbers\\
		\hline
	\end{tabular}
\caption{Description and characteristics of benchmark applications used to
evaluate \sys.}
\label{table:benchmark_table}
\end{table}
